---
title: "Actigraph Reliability Comparison"
output: html_notebook
---

## Coefficient of Agreement: Intraclass Corrolation Coefficient

* Interpreting ICC
  + Values less than 0.5 = poor reliability 
  + Values between 0.5 and 0.75 = moderate reliability
  + Values between 0.75 and 0.9 = good reliability
  + Values greater than 0.9 = excellent reliability

A Guideline of Selecting and Reporting Intraclass Correlation Coefficients for Reliability Research, Koo 2016 

* ICC type
  + ICC(1) Each subject is assessed by a different set of randomly selected raters, and the
  reliability is calculated from a single measurement. Uncommonly used in clinical
  reliability studies.
  + ICC(1,k) As above, but reliability is calculated by taking an average of the k raters’
  measurements.
  + ICC(2) Each subject is measured by each rater, and raters are considered representative
  of a larger population of similar raters. Reliability calculated from a single
  measurement.
  + ICC(2,k) As above, but reliability is calculated by taking an average of the k raters’
  measurements.
  + ICC(3) Each subject is assessed by each rater, but the raters are the only raters of
  interest. Reliability calculated from a single measurement.
  + ICC(3,k) As above, but reliability is calculated by taking an average of the k raters’
  measurements.
    + Please note that subjects in this case are nights of sleep and raters are the two actigraphs
  
Model ICC(2) appears most applicable to the sleep data set

## GENEActiv data {.tabset}

### Load Data
```{r}
#Set current working directory
setwd("~/Desktop/sleepdata")

#Import data for total time in bed
library(readr)
GSLEEP <- read_csv("GSLEEP.csv")

#View(GSLEEP)
GSLEEP
```
### Time in Bed (dur)

```{r}
#Select Columns of Data Table
library(dplyr)
dur <- select(GSLEEP, durg1, durg2)
durdiary <- select(GSLEEP, durg1, durg2, durd)

#Intraclass Correlation Coefficient
library(psych)
ICC(dur, missing = TRUE, alpha = 0.05, lmer = TRUE, check.keys = FALSE )
ICC(durdiary, missing = TRUE, alpha = 0.05, lmer = TRUE, check.keys = FALSE )
#Plot
boxplot (durdiary$durg1, durdiary$durg2, durdiary$durd, col=terrain.colors(3), at=c(1,2,3), names = c("GENEActiv 1", "GENEActiv 2", "Diary"))
title (main = "Time in Bed", ylab = "Time (mins)", xlab = "Tracking Method", font.lab = 2)

plot(dur$durg1, dur$durg2, xlab= "GENEActiv 1 (mins)", ylab = "GENEActiv 2 (mins)", main= "Time in Bed")
```
##### Time in bed (dur) has an **ICC2 of 0.90** indicating **good-excellent reliability** between actigraphs where sleep assessment data on time spent in bed is  corrolated between GENEActiv Devices.
##### Time in bed (dur) has an **ICC2 of 0.89** indicating **good reliability** between actigraphs and sleep diary where sleep assessment data on time spent in bed is corrolated between GENEActiv Devices and sleep diary.

### Percent Sleep (pslp)
#### PSLP = (Sleep Minutes / Duration in Bed) x 100
```{r}
# Select Columns of Data Table
library(dplyr)
pslp <- select(GSLEEP, pslpg1, pslpg2)

# Intraclass Correlation Coefficient
library(psych)
ICC(pslp, missing = TRUE, alpha = 0.05, lmer = TRUE, check.keys = FALSE )

#Plot
boxplot (pslp$pslpg1, pslp$pslpg2, col=terrain.colors(2), at=c(1,2), names = c("GENEActiv 1", "GENEActiv 2"))
title (main = "Percent Sleep", ylab = "Sleep in Minutes/ Duration in Bed * 100", xlab = "Tracking Method", font.lab = 2)

plot(pslp$pslpg1, pslp$pslpg2, xlab= "GENEActiv 1 (percent)", ylab = "GENEActiv 2 (percent)", main= "Percent Sleep")
```
##### Percent Sleep (pslp) has an **ICC2 of 0** indicating **no reliability** between actigraphs where sleep assessment data on percent sleep is NOT corrolated between GENEActiv Devices within the current dataset.

### Sleep Minutes (smin)
```{r}
# Select Columns of Data Table
library(dplyr)
smin <- select(GSLEEP, sming1, sming2)
smindiary <- select(GSLEEP, sming1, sming2, smind)

# Intraclass Correlation Coefficient
library(psych)
ICC(smin, missing = TRUE, alpha = 0.05, lmer = TRUE, check.keys = FALSE )
ICC(smindiary, missing = TRUE, alpha = 0.05, lmer = TRUE, check.keys = FALSE )

#Plot
boxplot (smindiary$sming1, smindiary$sming2, smindiary$smind, col=terrain.colors(3), at=c(1,2,3), names = c("GENEActiv 1", "GENEActiv 2", "Diary"))
title(main = "Total Sleep Minutes", ylab = "Time (mins)", xlab = "Tracking Method", font.lab = 2)

plot(smin$sming1, smin$sming2, xlab= "GENEActiv 1 (mins)", ylab = "GENEActiv 2 (mins)", main= "Total Sleep Minutes")
```
##### Sleep minutes (smin) has an **ICC2 of 0.72** indicating **moderate reliability** between actigraphs where sleep assessment data on sleep minutes is corrolated between GENEActiv Devices.
##### Sleep minutes (smin) has an **ICC2 of 0.70** indicating **moderate reliability** between actigraphs and sleep diary where sleep assessment data on sleep minutes is corrolated between GENEActiv Devices and sleep diary.

### Wake Minutes (wmin)
```{r}
# Select Columns of Data Table
library(dplyr)
wmin <- select(GSLEEP, wming1, wming2)
wmindiary <- select(GSLEEP, wming1, wming2, wmind)

# Intraclass Correlation Coefficient
library(psych)
ICC(wmin, missing = TRUE, alpha = 0.05, lmer = TRUE, check.keys = FALSE )
ICC(wmindiary, missing = TRUE, alpha = 0.05, lmer = TRUE, check.keys = FALSE )

#Plot
boxplot (wmin$wming1, wmin$wming2, wmindiary$wmind, col=terrain.colors(3), at=c(1,2,3), names = c("GENEActiv 1", "GENEActiv 2","Diary"))
title(main = "Wake Minutes", ylab = "Time (mins)", xlab = "Tracking Method", font.lab = 2)

plot(wmin$wming1, wmin$wming2, xlab= "GENEActiv 1 (mins)", ylab = "GENEActiv 2 (mins)", main= "Wake Minutes")
```
##### Wake minutes (wmin) has an **ICC2 of 0** indicating **no reliability** between actigraphs where sleep assessment data on total wake minutes in bed is NOT corrolated between GENEActiv Devices within the current data set.
##### Wake minutes (wmin) has an **ICC2 of 0** indicating **no reliability** between actigraphs and sleep diary where sleep assessment data on total wake minutes in bed is NOT corrolated between GENEActiv Devices and sleep diary within the current data set.

### Wake-up time (etime)
#### Adjusted to 2pm = 0:00 in minutes since 2pm
```{r}
# Select Columns of Data Table
library(dplyr)
etime <- select(GSLEEP, etimeg1, etimeg2)

#Adjust time & create data frame with time in minutes since 2pm
library("lubridate")
etime<- c(etime$etimeg1, etime$etimeg2)

library(lubridate)
res <- hms(etime)       
time <- hour(res)*60 + minute(res) + 600 

time

etime.df <- data.frame(matrix(time, nrow=7, ncol=2))
colnames(etime.df) <- c("etimeg1a", "etimeg2a")
etime.df

etime.df %>%
  mutate_all(funs(ifelse(.>1439, .-1440, .)))

#Calculate Intraclass Correlation
library(psych)
ICC(etime.df, missing = TRUE, alpha = 0.05, lmer = TRUE, check.keys = FALSE )

#Repeat with Diary
# Select Columns of Data Table
library(dplyr)
etimediary <- select(GSLEEP, etimeg1, etimeg2, etimed)

#Adjust time & create data frame with time in minutes since 2pm
library("lubridate")
etimediary<- c(etimediary$etimeg1, etimediary$etimeg2, etimediary$etimed)

library(lubridate)
res <- hms(etimediary)       
time <- hour(res)*60 + minute(res) + 600 

time

etimediary.df <- data.frame(matrix(time, nrow=7, ncol=3))
colnames(etimediary.df) <- c("etimeg1a", "etimeg2a", "etimeda")
etimediary.df

etimediary.df %>%
  mutate_all(funs(ifelse(.>1439, .-1440, .)))

#Calculate Intraclass Correlation
library(psych)
ICC(etimediary.df, missing = TRUE, alpha = 0.05, lmer = TRUE, check.keys = FALSE )

#Plot
boxplot (etime.df$etimeg1a, etime.df$etimeg2a, etimediary.df$etimeda, col=terrain.colors(3), at=c(1,2,3), names = c("GENEActiv 1", "GENEActiv 2", "Diary"))
title(main = "Wake-up Time", ylab = "Time (mins after 2pm)", xlab = "Tracking Method", font.lab = 2)

plot(etime.df$etimeg1, etime.df$etimeg2, xlab= "GENEActiv 1 (mins since 2pm)", ylab = "GENEActiv 2 (mins since 2pm)", main= "Wake-up Time")

```
##### Wake-up Time (etime) has an **ICC2 of 0.86** indicating **good reliability** between actigraphs where sleep assessment data on wake-up time is corrolated between GENEActiv Devices.
##### Wake-up Time (etime) has an **ICC2 of 0.79** indicating **good reliability** between actigraphs and sleep diary where sleep assessment data on wake-up Ttme is corrolated between GENEActiv Devices and sleep diary.

### Sleep Time (stime)
#### Adjusted to 2pm = 0:00 in mins since 2pm
```{r}
# Select Columns of Data Table
library(dplyr)
stime <- select(GSLEEP, stimeg1, stimeg2)

#Adjust time & create data frame with time in minutes since 2pm
library("lubridate")
stime<- c(stime$stimeg1, stime$stimeg2)

library(lubridate)
res <- hms(stime)       
time <- hour(res)*60 + minute(res) + 600 

time

stime.df <- data.frame(matrix(time, nrow=7, ncol=2))
colnames(stime.df) <- c("stimeg1a", "stimeg2a")
stime.df

stime.df %>%
  mutate_all(funs(ifelse(.>1439, .-1440, .)))

#Calculate Intraclass Correlation
library(psych)
ICC(stime.df, missing = TRUE, alpha = 0.05, lmer = TRUE, check.keys = FALSE )

#Repeat with Diary
# Select Columns of Data Table
library(dplyr)
stimediary <- select(GSLEEP, stimeg1, stimeg2, stimed)

#Adjust time & create data frame with time in minutes since 2pm
library("lubridate")
stimediary<- c(stimediary$stimeg1, stimediary$stimeg2, stimediary$stimed)

library(lubridate)
res <- hms(stimediary)       
time <- hour(res)*60 + minute(res) + 600 

time

stimediary.df <- data.frame(matrix(time, nrow=7, ncol=3))
colnames(stimediary.df) <- c("stimeg1a", "stimeg2a","stimeda")
stimediary.df

stimediary.df %>%
  mutate_all(funs(ifelse(.>1439, .-1440, .)))

#Calculate Intraclass Correlation
library(psych)
ICC(stimediary.df, missing = TRUE, alpha = 0.05, lmer = TRUE, check.keys = FALSE )

#Plot
boxplot (stime.df$stimeg1a, stime.df$stimeg2a, stimediary.df$stimeda, col=terrain.colors(3), at=c(1,2,3), names = c("GENEActiv 1", "GENEActiv 2", "Diary"))
title(main = "Sleep Time", ylab = "Time (mins after 2pm)", xlab = "Tracking Method", font.lab = 2)

plot(stime.df$stimeg1, stime.df$stimeg2, xlab= "GENEActiv 1 (mins since 2pm)", ylab = "GENEActiv 2 (mins since 2pm)", main= "Sleep Time")
```
##### Sleep Time (stime) has an **ICC2 of 0.70** indicating **moderate reliability** between actigraphs where sleep assessment data on sleep time is corrolated between GENEActiv Devices.
##### Sleep Time (stime) has an **ICC2 of 0.51** indicating **moderate reliability** between actigraphs and sleep diary where sleep assessment data on sleep time is corrolated between GENEActiv Devices and sleep diary.




## Motionlogger data {.tabset}

### Load Data
```{r}
# set current working directory
setwd("~/Desktop/sleepdata")

# import data for total time in bed
library(readr)
MSLEEP <- read_csv("MSLEEP.csv")

# View(MSLEEP)
MSLEEP
```

### Time in Bed (dur)
```{r}
#Select Columns of Data Table
library(dplyr)
dur <- select(MSLEEP, durm1, durm2)
durdiary <- select(MSLEEP, durm1, durm2, durd)

#Intraclass Correlation Coefficient
library(psych)
ICC(dur, missing = TRUE, alpha = 0.05, lmer = TRUE, check.keys = FALSE )
ICC(durdiary, missing = TRUE, alpha = 0.05, lmer = TRUE, check.keys = FALSE )
#Plot
boxplot (dur$durm1, dur$durm2, durdiary$durd, col=terrain.colors(3), at=c(1,2,3), names = c("Motionlogger 1", "Motionlogger 2", "Diary"))
title(ylab = "Time in Bed (mins)", xlab = "Tracking Method", font.lab = 2)

plot(dur$durm1, dur$durm2, xlab= "Motionlogger 1 (mins)", ylab = "Motionlogger 2 (mins)", main= "Time in Bed")
```
##### Time in bed (duration) has an **ICC2 of 0.999** indicating **excellent** reliability between actigraphs where sleep assessment data on time spent in bed is corrolated between Motionlogger Devices.
##### Time in bed (duration) has an **ICC2 of 0.298** indicating **poor** reliability between actigraphs and sleep diary where sleep assessment data on time spent in bed is NOT corrolated between Motionlogger Devices and sleep diary.

### Percent Sleep (pslp)
```{r}
# Select Columns of Data Table
pslp <- select(MSLEEP, pslpm1, pslpm2)

# Intraclass Correlation Coefficient
library(psych)
ICC(pslp, missing = TRUE, alpha = 0.05, lmer = TRUE, check.keys = FALSE )

# Plot
boxplot (pslp$pslpm1, pslp$pslpm2, col=terrain.colors(2), at=c(1,2), names = c("Motionlogger 1", "Motionlogger 2"))
title(ylab = "Percent Sleep", xlab = "Tracking Method", font.lab = 2)

plot(pslp$pslpm1, pslp$pslpm2, xlab= "Motionlogger 1 (percent)", ylab = "Motionlogger 2 (percent)", main= "Percent Sleep")

```
##### Percent Sleep (pslp) has an **ICC2 of 0.985** indicating **excellent** reliability between actigraphs where sleep assessment data on percent sleep is corrolated between Motionlogger Devices.

### Sleep Minutes (smin)
```{r}
# Select Columns of Data Table
library(dplyr)
smin <- select(MSLEEP, sminm1, sminm2)
smindiary <- select(MSLEEP, sminm1, sminm2, smind)

# Intraclass Correlation Coefficient
library(psych)
ICC(smin, missing = TRUE, alpha = 0.05, lmer = TRUE, check.keys = FALSE )
ICC(smindiary, missing = TRUE, alpha = 0.05, lmer = TRUE, check.keys = FALSE )

#Plot
boxplot (smindiary$sminm1, smindiary$sminm2, smindiary$smind, col=terrain.colors(3), at=c(1,2,3), names = c("Motionlogger 1", "Motionlogger 2", "Diary"))
title(main = "Total Sleep Minutes", ylab = "Time (mins)", xlab = "Tracking Method", font.lab = 2)

plot(smin$sminm1, smin$sminm2, xlab= "Motionlogger 1 (mins)", ylab = "Motionlogger 2 (mins)", main= "Total Sleep Minutes")
```
##### Total Minutes of Sleep (smin) has an **ICC2 of 0.999** indicating **excellent** reliability between actigraphs where sleep assessment data on sleep minutes is corrolated between Motionlogger Devices.
##### Total Minutes of Sleep (smin) has an **ICC2 of 0.326** indicating **poor** reliability between actigraphs and sleep diary where sleep assessment data on sleep minutes is NOT corrolated between Motionlogger Devices and sleep diary.

### Wake Minutes (wmin)
```{r}
# Select Columns of Data Table
library(dplyr)
wmin <- select(MSLEEP, wminm1, wminm2)
wmindiary <- select(MSLEEP, wminm1, wminm2, wmind)

# Intraclass Correlation Coefficient
library(psych)
ICC(wmin, missing = TRUE, alpha = 0.05, lmer = TRUE, check.keys = FALSE )
ICC(wmindiary, missing = TRUE, alpha = 0.05, lmer = TRUE, check.keys = FALSE )

#Plot
boxplot (wmin$wminm1, wmin$wminm2, wmindiary$wmind, col=terrain.colors(3), at=c(1,2,3), names = c("Motionlogger 1", "Motionlogger 2","Diary"))
title(main = "Wake Minutes", ylab = "Time (mins)", xlab = "Tracking Method", font.lab = 2)

plot(wmin$wminm1, wmin$wminm2, xlab= "Motionlogger 1 (mins)", ylab = "Motionlogger 2 (mins)", main= "Wake Minutes")
```
##### Total Minutes of Wake has an **ICC2 of 0.984** indicating **excellent** reliability between actigraphs where sleep assessment data on total wake minutes in bed is corrolated between Motionlogger Devices
##### Total Minutes of Wake has an **ICC2 of 1.5*10^-4** indicating **poor** reliability between actigraphs and sleep diary where sleep assessment data on total wake minutes in bed is corrolated between Motionlogger Devices

### Wake After Sleep Onset (waso)
```{r}
library(dplyr)
waso <- select(MSLEEP, wasom1, wasom2)

# Intraclass Correlation Coefficient
library(psych)

ICC(waso, missing = TRUE, alpha = 0.05, lmer = TRUE, check.keys = FALSE )

#Plot
boxplot (waso$wasom1, waso$wasom2, col=terrain.colors(2), at=c(1,2), names = c("Motionlogger 1", "Motionlogger 2"))
title(ylab = "Wake after sleep onset (mins)", xlab = "Tracking Method", font.lab = 2)

plot(waso$wasom1, waso$wasom2, xlab= "Motionlogger 1 (mins)", ylab = "Motionlogger 2 (mins)", main= "Wake After Sleep Onset")
```
##### Wake after sleep onset (waso) has an **ICC2 of 0.868** indicating **good** reliability between actigraphs where sleep assessment data on wake after sleep onset is corrolated between Motionlogger Devices

### Wake-up Time (etime)
#### Adjusted to 2pm = 0:00 in mins since 2pm
```{r}
# Select Columns of Data Table
library(dplyr)
etime <- select(MSLEEP, etimem1, etimem2)

#Adjust time & create data frame with time in minutes since 2pm
library("lubridate")
etime<- c(etime$etimem1, etime$etimem2)

library(lubridate)
res <- hms(etime)       
time <- hour(res)*60 + minute(res) + 600 

time

etime.df <- data.frame(matrix(time, nrow=7, ncol=2))
colnames(etime.df) <- c("etimem1a", "etimem2a")
etime.df

etime.df %>%
  mutate_all(funs(ifelse(.>1439, .-1440, .)))

#Calculate Intraclass Correlation
library(psych)
ICC(etime.df, missing = TRUE, alpha = 0.05, lmer = TRUE, check.keys = FALSE )

#Repeat with Diary
# Select Columns of Data Table
library(dplyr)
etimediary <- select(MSLEEP, etimem1, etimem2, etimed)

#Adjust time & create data frame with time in minutes since 2pm
library("lubridate")
etimediary<- c(etimediary$etimem1, etimediary$etimem2, etimediary$etimed)

library(lubridate)
res <- hms(etimediary)       
time <- hour(res)*60 + minute(res) + 600 

time

etimediary.df <- data.frame(matrix(time, nrow=7, ncol=3))
colnames(etimediary.df) <- c("etimem1a", "etimem2a", "etimeda")
etimediary.df

etimediary.df %>%
  mutate_all(funs(ifelse(.>1439, .-1440, .)))

#Calculate Intraclass Correlation
library(psych)
ICC(etimediary.df, missing = TRUE, alpha = 0.05, lmer = TRUE, check.keys = FALSE )

#Plot
boxplot (etime.df$etimem1a, etime.df$etimem2a, etimediary.df$etimeda, col=terrain.colors(3), at=c(1,2,3), names = c("Motionlogger 1", "Motionlogger 2", "Diary"))
title(main = "Wake-up Time", ylab = "Time (mins after 2pm)", xlab = "Tracking Method", font.lab = 2)

plot(etime.df$etimem1, etime.df$etimem2, xlab= "Motionlogger 1 (mins since 2pm)", ylab = "Motionlogger 2 (mins since 2pm)", main= "Wake-up Time")
```
##### Wake up time (etime) has an **ICC2 of 0.999** indicating **excellent** reliability between actigraphs where sleep assessment data on wake-up time is corrolated between Motionlogger Devices.
##### Wake up time (etime) has an **ICC2 of 0.872** indicating **good** reliability between actigraphs and sleep diary where sleep assessment data on wake-up time is corrolated between Motionlogger Devices and sleep diary.

### Sleep Time (stime)
#### Adjusted to 2pm = 0:00 in mins since 2pm
```{r}
# Select Columns of Data Table
library(dplyr)
stime <- select(MSLEEP, stimem1, stimem2)

#Adjust time & create data frame with time in minutes since 2pm
library("lubridate")
stime<- c(stime$stimem1, stime$stimem2)

library(lubridate)
res <- hms(stime)       
time <- hour(res)*60 + minute(res) + 600 

time

stime.df <- data.frame(matrix(time, nrow=7, ncol=2))
colnames(stime.df) <- c("stimem1a", "stimem2a")
stime.df

stime.df %>%
  mutate_all(funs(ifelse(.>1439, .-1440, .)))

#Calculate Intraclass Correlation
library(psych)
ICC(stime.df, missing = TRUE, alpha = 0.05, lmer = TRUE, check.keys = FALSE )

#Repeat with Diary
# Select Columns of Data Table
library(dplyr)
stimediary <- select(MSLEEP, stimem1, stimem2, stimed)

#Adjust time & create data frame with time in minutes since 2pm
library("lubridate")
stimediary<- c(stimediary$stimem1, stimediary$stimem2, stimediary$stimed)

library(lubridate)
res <- hms(stimediary)       
time <- hour(res)*60 + minute(res) + 600 

time

stimediary.df <- data.frame(matrix(time, nrow=7, ncol=3))
colnames(stimediary.df) <- c("stimem1a", "stimem2a","stimeda")
stimediary.df

stimediary.df %>%
  mutate_all(funs(ifelse(.>1439, .-1440, .)))

#Calculate Intraclass Correlation
library(psych)
ICC(stimediary.df, missing = TRUE, alpha = 0.05, lmer = TRUE, check.keys = FALSE )

#Plot
boxplot (stime.df$stimem1a, stime.df$stimem2a, stimediary.df$stimeda, col=terrain.colors(3), at=c(1,2,3), names = c("Motionlogger 1", "Motionlogger 2", "Diary"))
title(main = "Sleep Time", ylab = "Time (mins after 2pm)", xlab = "Tracking Method", font.lab = 2)

plot(stime.df$stimem1, stime.df$stimem2, xlab= "Motionlogger 1 (mins since 2pm)", ylab = "Motionlogger 2 (mins since 2pm)", main= "Sleep Time")
```
##### Sleep Time (stime) has an **ICC2 of 1** indicating **complete reliability** between actigraphs where sleep assessment data on sleep time is perfectly corrolated between Motionlogger Devices.
##### Sleep Time (stime) has an **ICC2 of 0.30** indicating **poor reliability** between actigraphs and sleep diary where sleep assessment data on sleep time is NOT corrolated between Motionlogger Devices and sleep diary.



## Motionlogger vs GENEActive data {.tabset}

### Time in Bed (dur)
```{r}
# set current working directory
setwd("~/Desktop/sleepdata")

# import data for total time in bed
library(readr)
dur <- read_csv("TinBed.csv")

# View(dur)
dur

library(psych)
ICC(dur, missing = TRUE, alpha = 0.05, lmer = TRUE, check.keys = FALSE )

library(dplyr)
dur_mg <- select(dur, durg, durm)
dur_dm <- select(dur, durd, durm)
dur_dg <- select(dur, durd, durg)

ICC(dur_mg, missing = TRUE, alpha = 0.05, lmer = TRUE, check.keys = FALSE )
ICC(dur_dm, missing = TRUE, alpha = 0.05, lmer = TRUE, check.keys = FALSE )
ICC(dur_dg, missing = TRUE, alpha = 0.05, lmer = TRUE, check.keys = FALSE )

#Plot
boxplot (dur$durd, dur$durm, dur$durg, col=terrain.colors(3), at=c(1,2,3), names = c("Diary", "Motionlogger", "GENEActiv"))
title(ylab = "Time in Bed (mins)", xlab = "Tracking Method", font.lab = 2)
```
##### Time in bed has an **ICC2 of 0.45** indicating **poor reliability** between actigraphs and sleep diary where sleep assessment data on time spent in bed is NOT corrolated between all 3 measures
##### Time in bed has an **ICC2 of 0.75** indicating **moderate-good reliability** between the 2 actigraphs where sleep assessment data on time spent in bed is corrolated between devices
##### Time in bed has an **ICC2 of 0.26** indicating **poor reliability** between Motionlogger actigraph and sleep diary where sleep assessment data on time spent in bed is NOT corrolated between measures
##### Time in bed has an **ICC2 of 0.29** indicating **poor reliability** between GENEActiv actigraph and sleep diary where sleep assessment data on time spent in bed is NOT corrolated between measures


### Percent Sleep (pslp) 
#### PSLP = (Sleep Minutes / Duration in Bed) x 100

```{r}
# Set current working directory
setwd("~/Desktop/sleepdata")

# Import data and perform analysis
library(readr)
pslp<- read_csv("PSLP.csv")

pslp

library(psych)
ICC(pslp, missing = FALSE, alpha = 0.05, lmer = TRUE, check.keys = FALSE )

library(dplyr)
pslp_mg <- select(pslp, pslpg, pslpm)
pslp_dm <- select(pslp, pslpd, pslpm)
pslp_dg <- select(pslp, pslpd, pslpg)

ICC(pslp_mg, missing = TRUE, alpha = 0.05, lmer = TRUE, check.keys = FALSE )
ICC(pslp_dm, missing = FALSE, alpha = 0.05, lmer = TRUE, check.keys = FALSE )
ICC(pslp_dg, missing = FALSE, alpha = 0.05, lmer = TRUE, check.keys = FALSE )

#Plot
boxplot (pslp$pslpd, pslp$pslpm, pslp$pslpg, col=terrain.colors(3), at=c(1,2,3), names = c("Diary", "Motionlogger", "GENEActiv"))
title(ylab = "Percent Sleep (%)", xlab = "Tracking Method", font.lab = 2)
```
##### Percent sleep has an **ICC2 of 0.10** indicating **poor reliability** between actigraphs and sleep diary where sleep assessment data on percent sleep is NOT corrolated between all 3 measures
##### Percent sleep has an **ICC2 of 0.033** indicating **poor reliability** between the 2 actigraphs where sleep assessment data on percent sleep is NOT corrolated between devices
##### Percent sleep has an **ICC2 of 0.053** indicating **poor reliability** between Motionlogger actigraph and sleep diary where sleep assessment data on percent sleep is NOT corrolated between devices
##### Percent sleep has an **ICC2 of 0.18** indicating **poor reliability** between GENEActiv actigraph and sleep diary where sleep assessment data on percent sleep is NOT corrolated between devices

### Sleep Minutes (smin)

```{r}
# set current working directory
setwd("~/Desktop/sleepdata")

#Minutes asleep in bed
library(readr)
smin <- read_csv("SMIN.csv")
smin

library(psych)
ICC(smin, missing = TRUE, alpha = 0.05, lmer = TRUE, check.keys = FALSE )

library(dplyr)
smin_mg <- select(smin, sming, sminm)
smin_dm <- select(smin, smind, sminm)
smin_dg <- select(smin, smind, sming)

ICC(smin_mg, missing = TRUE, alpha = 0.05, lmer = TRUE, check.keys = FALSE )
ICC(smin_dm, missing = TRUE, alpha = 0.05, lmer = TRUE, check.keys = FALSE )
ICC(smin_dg, missing = TRUE, alpha = 0.05, lmer = TRUE, check.keys = FALSE )

#Plot
boxplot (smin$smind, smin$sminm, smin$sming, col=terrain.colors(3), at=c(1,2,3), names = c("Diary", "Motionlogger", "GENEActiv"))
title(ylab = "Total Sleep Time (mins)", xlab = "Tracking Method", font.lab = 2)
```
##### Sleep minutes has an **ICC2 of 0.089** indicating **poor reliability** between actigraphs and sleep diary where sleep assessment data on sleep minutes is NOT corrolated between all 3 measures
##### Sleep minutes has an **ICC2 of 0.238** indicating **poor reliability** between the 2 actigraphs where sleep assessment data on sleep minutes is NOT corrolated between devices
##### Sleep minutes has an **ICC2 of 0.027** indicating **poor reliability** between Motionlogger actigraph and sleep diary where sleep assessment data on sleep minutes is NOT corrolated between devices
##### Sleep minutes has an **ICC2 of 2.1*10^-10** indicating **poor reliability** between GENEActiv actigraph and sleep diary where sleep assessment data on sleep minutes is NOT corrolated between devices


### Wake Minutes (wmins)

```{r}
# set current working directory
setwd("~/Desktop/sleepdata")

#minutes awake in bed
library(readr)
wmin <- read_csv("WMIN.csv")
wmin

library(psych)
ICC(wmin, missing = TRUE, alpha = 0.05, lmer = TRUE, check.keys = FALSE )

library(dplyr)
wmin_mg <- select(wmin, wming, wminm)
wmin_dm <- select(wmin, wmind, wminm)
wmin_dg <- select(wmin, wmind, wming)

ICC(wmin_mg, missing = TRUE, alpha = 0.05, lmer = TRUE, check.keys = FALSE )
ICC(wmin_dm, missing = TRUE, alpha = 0.05, lmer = TRUE, check.keys = FALSE )
ICC(wmin_dg, missing = TRUE, alpha = 0.05, lmer = TRUE, check.keys = FALSE )

#Plot
boxplot (wmin$wmind, wmin$wminm, wmin$wming, col=terrain.colors(3), at=c(1,2,3), names = c("Diary", "Motionlogger", "GENEActiv"))
title(ylab = "Total Wake Time in Bed (mins)", xlab = "Tracking Method", font.lab = 2)
```
##### Wake minutes has an **ICC2 of 0.23** indicating **poor reliability** between actigraphs and sleep diary where sleep assessment data on wake minutes is NOT corrolated between all 3 measures
##### Wake minutes has an **ICC2 of 0.027** indicating **poor reliability** between the 2 actigraphs where sleep assessment data on wake mintues is NOT corrolated between devices.
##### Wake minutes has an **ICC2 of 0.11** indicating **poor reliability** between Motionlogger actigraph and sleep diary where sleep assessment data on wake minutes is NOT corrolated between devices
##### Wake minutes has an **ICC2 of 0.46** indicating **poor reliability** between GENEActiv actigraph and sleep diary where sleep assessment data on wake minutes is NOT corrolated between devices

### Sleep Time
```{r}
# set current working directory
setwd("~/Desktop/sleepdata")

library(readr)
adjbtime <- read_csv("adjbtime.csv")

library("lubridate")
mbtime<- c(adjbtime$adjbtimed, adjbtime$adjbtimem, adjbtime$adjbtimeg)

library(lubridate)
res <- hms(mbtime)       
hour(res)*60 + minute(res)       

mbtimed <- c(630, 660, 700,  NA, 555, 520, 733, 510, 540, 630, 630, NA, 630, 780)
mbtimem <- c(525, 631, 648, 558, 537, 542, 727, 519, 541, 627, 638, 645, 634, 787)
mbtimeg <- c(544, 664, 658, 557, 546, 547, 725, 522, 544, 626, 638, 644, 636, 787)

mbtime <- data.frame(mbtimed, mbtimem, mbtimeg)
mbtime
   
```

```{r}
#Bedtime adjusted to 2pm = 0:00 in mins since 2pm
library(psych)
ICC(mbtime, missing = TRUE, alpha = 0.05, lmer = TRUE, check.keys = FALSE )

library(dplyr)
mbtime_mg <- select(mbtime, mbtimeg, mbtimem)
mbtime_dm <- select(mbtime, mbtimed, mbtimem)
mbtime_dg <- select(mbtime, mbtimed, mbtimeg)

ICC(mbtime_mg, missing = TRUE, alpha = 0.05, lmer = TRUE, check.keys = FALSE )
ICC(mbtime_dm, missing = TRUE, alpha = 0.05, lmer = TRUE, check.keys = FALSE )
ICC(mbtime_dg, missing = TRUE, alpha = 0.05, lmer = TRUE, check.keys = FALSE )

boxplot (mbtime$mbtimed, mbtime$mbtimem, mbtime$mbtimeg, col=terrain.colors(3), at=c(1,2,3), names = c("Diary", "Motionlogger", "GENEActiv"))
title(ylab = "Bedtime (mins after 2pm)", xlab = "Tracking Method", font.lab = 2)
```
##### Sleep time has an **ICC2 of 0.94** indicating **excellent reliability** between actigraphs and sleep diary where sleep assessment data on sleep time is corrolated between all 3 measures
##### Sleep time has an **ICC2 of 0.99** indicating **excellent reliability** between the 2 actigraphs where sleep assessment data on sleep time is corrolated between devices.
##### Sleep time has an **ICC2 of 0.90** indicating **excellent reliability** between Motionlogger actigraph and sleep diary where sleep assessment data on sleep time is  corrolated between devices
##### Sleep time has an **ICC2 of 0.93** indicating **excellent reliability** between GENEActiv actigraph and sleep diary where sleep assessment data on sleep time is corrolated between devices

### Wake-up time
```{r}
# set current working directory
setwd("~/Desktop/sleepdata")

library(readr)
adjwtime <- read_csv("adjwtime.csv")

library("lubridate")
mwtime<- c(adjwtime$adjwtimed, adjwtime$adjwtimem, adjwtime$adjwtimeg)

library(lubridate)
res <- hms(mwtime)       
hour(res)*60 + minute(res)       

mwtimed <- c(1020, 1050, 1100, NA, 990, 960, 1080, 1020,  990, 1050, 1035, 1110, 1065, 1065)
mwtimem <- c(1019, 1113, 1145, 990, 990, 957, 1077, 986, 990, 1050, 1038, 1110, 1065, 1067)
mwtimeg <- c(1057, 1113, 1102, 992, 990, 957, 1106, 982, 991, 1040, 1038, 1075, 1072, 1131)

mwtime <- data.frame(mwtimed, mwtimem, mwtimeg)
mwtime

```

#### Wake up time adjusted to 2pm = 0:00 in mins since 2pm

```{r}
#Wake up time adjusted to 2pm = 0:00
library(psych)
ICC(mwtime, missing = TRUE, alpha = 0.05, lmer = TRUE, check.keys = FALSE )

library(dplyr)
mwtime_mg <- select(mwtime, mwtimeg, mwtimem)
mwtime_dm <- select(mwtime, mwtimed, mwtimem)
mwtime_dg <- select(mwtime, mwtimed, mwtimeg)

ICC(mwtime_mg, missing = TRUE, alpha = 0.05, lmer = TRUE, check.keys = FALSE )
ICC(mwtime_dm, missing = TRUE, alpha = 0.05, lmer = TRUE, check.keys = FALSE )
ICC(mwtime_dg, missing = TRUE, alpha = 0.05, lmer = TRUE, check.keys = FALSE )

boxplot (mwtime$mwtimed, mwtime$mwtimem, mwtime$mwtimeg, col=terrain.colors(3), at=c(1,2,3), names = c("Diary", "Motionlogger", "GENEActiv"))
title(ylab = "Waketime (mins after 2pm)", xlab = "Tracking Method", font.lab = 2)
```
##### Wake-up time has an **ICC2 of 0.86** indicating **good reliability** between actigraphs and sleep diary where sleep assessment data on wake-up time is corrolated between all 3 measures
##### Wake-up time has an **ICC2 of 0.89** indicating **good reliability** between the 2 actigraphs where sleep assessment data on wake-up time is  corrolated between devices.
##### Wake-up time has an **ICC2 of 0.89** indicating **good reliability** between Motionlogger actigraph and sleep diary where sleep assessment data on wake-up time is  corrolated between devices
##### Wake-up time has an **ICC2 of 0.80** indicating **good reliability** between GENEActiv actigraph and sleep diary where sleep assessment data on wake-up time is corrolated between devices